CRUSE to Safe Cycling in Ireland

### 2023-09-19 paper.qmd
Add anable reference

Uptake of cycling, the main topic of this paper, should be seen in this broader context of transport decarbonisation [@brand2020] and sustainable mobility [@burns2013].
Although cycling uptake appears on the surface to only relate to the 'shift' part of the ASI framework, closer consideration of the knock-on impacts of cycling uptake shows that it can also help avoid unnecessary trips [@nello-deakin2020].
The rapid uptake of highly efficient e-bikes can also be seen as an improvement on most electric vehicles, which are too heavy and expensive to be a sustainable alternative and could in fact delay the transition away from car dependency and inadvertently enable "high travel lock-in" [@shifting].

>>>>

Uptake of cycling, the main topic of this paper, should be seen in this broader context of transport decarbonisation [@brand2020] and sustainable mobility [@burns2013].
Although cycling uptake appears on the surface to only relate to the 'shift' part of the ASI framework, closer consideration of the knock-on impacts of cycling uptake shows that it can also help avoid unnecessary trips [@nello-deakin2020].
The rapid uptake of highly efficient e-bikes can also be seen as an improvement on most electric vehicles, which are too heavy and expensive to be a sustainable alternative and could in fact delay the transition away from car dependency and inadvertently enable "high travel lock-in" [@anable2019].
